---
title: "Challenge-5"
author: "Ho Wei Ni"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
x <- 5
print(x)

new_x <- function(x) {
  x <- 10
  return(x)
}
new_x()
x
```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
total <- 0

accumulated_total <- function(value) {
  total + value
}

total <- accumulated_total(5)
total <- accumulated_total(10)
total <- accumulated_total(90)
total
```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
total <- 100
add_to_total <- function(x) {
  total <- total + x
}

total <- add_to_total(200)
total <- add_to_total(20)
total
```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
outer_function <- function() {
  x <- 5
  
  inner_function <- function() {
    print(x)
  }
  
  inner_function()
}

outer_function()

```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
library(magick)
meme_generator <- function(text_input) {
  img <- image_read('thisisfinetemplate.jpeg')
  #img<- image_annotate(img, text_input, size = 70, gravity = "southwest", color = "green") 
  #image_annotate is not working :()
  print(img)
}

meme_generator("Hello")
```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
text_analysis_game <- function(sentence) {
  num_of_words <- length(strsplit(sentence, " ")[[1]])
  num_of_chars <- nchar(sentence)
  avg_word_length <- num_of_chars / num_of_words
  
  comm_skill_level <- ifelse(avg_word_length < 4, "Beginner",
                        ifelse(avg_word_length < 6, "Intermediate", "Advanced"))
  
  print(paste0("Number of words: ", num_of_words))
  print(paste0("Number of characters: ", num_of_chars))
  print(paste0("Average word length: ", avg_word_length))
  print(paste0("Your communication level is: ", comm_skill_level))
}

text_analysis_game("The quick brown fox jumps over the lazy dog in the backyard")
```
<br>