---
author: "Ho Wei Ni"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  df_print: paged
  html_document: null
title: "Week-5: Code-along"
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Writing a function
<br>

### 1. Write a function to print a "Hello" message (Slide #14)

```{r, eval=TRUE,echo=TRUE}
say_hello_to <- function(name) {
  print(paste0("Hello ", name, "!"))
}
```
<br>

### 2. Function call with different input names (Slide #15)

```{r, eval=TRUE,echo=TRUE}
say_hello_to("Panaree")
say_hello_to("Zi Qi")
say_hello_to("Kymie")
```
<br>

### 3. typeof primitive functions (Slide #16)

```{r, eval=TRUE,echo=TRUE}
typeof(`+`)
typeof(sum)
```
<br>

### 4. typeof user-defined functions (Slide #17)

```{r, eval=TRUE,echo=TRUE}
typeof(say_hello_to)
typeof(mean)
```
<br>

### 5. Function to calculate mean of a sample (Slide #19)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean <- function(sample_size) {
  mean(rnorm(sample_size))
}
```
<br>

### 6. Test your function (Slide #22)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean(200)
```
<br>
```{r, eval=TRUE,echo=TRUE}
calc_sample_mean(c(100,234,2987))
```
<br>

### 7. Customizing the function to suit input (Slide #23)

```{r, eval=TRUE,echo=TRUE}
library(tidyverse)
sample_tibble <- tibble(sample_sizes = 
                          c(100, 300, 3000))

sample_tibble %>% 
  group_by(sample_sizes) %>%
  mutate(sample_means = 
           calc_sample_mean(sample_sizes))
```
<br>

### 8. Setting defaults (Slide #25)

```{r, eval=TRUE,echo=TRUE}
# First define the function
calc_sample_mean <- function(sample_size, 
                             our_mean=0, 
                             our_sd=1) {
  sample <- rnorm(sample_size,
                  mean = our_mean,
                  sd = our_sd)
  
   mean(sample)
}
# Call the function 
calc_sample_mean(sample_size = 10)
```
<br>

### 9. Different input combinations (Slide #26)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean(10, our_sd = 2)
calc_sample_mean(10, our_mean = 10)
calc_sample_mean(10, 6, 2)
```
<br>

### 10. Different input combinations (Slide #27)

```{r, eval=TRUE,echo=TRUE,error=TRUE} 
# set error=TRUE to see the error message in the output
calc_sample_mean(our_mean = 5)
```
<br>

### 11. Some more examples (Slide #28)

```{r, eval=TRUE,echo=TRUE,error=FALSE} 
add_two <- function(x) {
  x+2
}

add_two(250)

divide_two <- function(x) {
  x/2
}

divide_two(250)
```
<br>

## B. Scoping
<br>

### 12. Multiple assignment of z (Slide #36)

```{r, eval=TRUE,echo=TRUE}
z <- 1
sprintf("The value assigned to z outside the function is %d",z)

foo <- function(z = 2) { 
  # reassigning z
  z <- 3
  return(z+3)
} 
foo()
```
<br>

### 13. Multiple assignment of z (Slide #37)

```{r, eval=TRUE,echo=TRUE}
z <- 1

foo <- function(z = 2) { 
  # reassigning z
  z <- 3
  return(z+3)
} 
foo(z = 5)

sprintf("The value assigned to z outside the function is %d",z)
```
<br>